\problemname{Mumble Rap}
\noindent
Willó listens to several different music genres and usually talks to both his friends about his favorite artists. 
One day, Willó asked his parents if they were willing to pay for a ticket to a music festival. 
The parents agreed to it at first, but his mother became quite hesitant when she realized that it was not just any music festival, but a mumble rap music festival!

\noindent
Willó's mother asked Willó how he could have an interest in such an incomprehensible music genre, as she found it difficult to identify numbers from words that the artist is mumbling. 
According to Willó's mother, mumble rap is known to be a genre where the artist always raps about how much money they own in a mumbling fashion. 
But Willó wanted to show love for mumble rap and prove his mother wrong, so he came up with the following plan: 
Willó wants to write a program that can identify the largest number in a string of characters that an artist has mumbled.

\section*{Input}
\noindent
The first line consists of an integer $1 \leqslant N \leqslant 10^6$, the number of characters in the string.
The second line consists of $N$ characters in a string without spaces, where each character is either a letter from ``a''-``z'',``A''-``Z'', a symbol (``.,;:?!''), or a digit between $0$ and $9$, including $0$ and $9$.

\section*{Output}
\noindent
Print an integer $0 \leqslant A \leqslant 10^9$ - The largest integer mentioned in the string. It is guaranteed that there is always a number in the string.


\section*{Grading}
\noindent
Your solution will be tested on a number of test-case groups.
To receive points for a group, your solution must correctly solve every test-case in the group.

\noindent
\begin{tabular}{| l | l | l |}
\hline
  Group & Point value & Constraints \\ \hline
  $1$    & $20$       &  $A \leqslant 9$ \\ \hline
  $2$    & $20$       &  The largest integer in the string is the last integer mentioned in the string. \\ \hline
  $3$    & $30$       &  $N \leqslant 10^3$ \\ \hline
  $4$    & $30$       &  No further restrictions \\ \hline
\end{tabular}
