\problemname{Triolingo Push}
\noindent
Trio from Triolingo wants to remind you to take your daily programming lessons!
\illustration{0.5}{triolingo}{cc by-s}

\noindent
To make sure you actually will complete your lesson every day, Trio sends you several notifications according to the following increasing pattern:

\noindent
On the first day, Trio sends $1$ notification.
On the second day, Trio sends $2$ notifications.
For each day after the second, the number of notifications is the number of notifications the day before, added with the number of notifications $2$ days ago, added with $1$ extra notification.
The number of notifications could also be described with the following recursive function:
$$f(1)=1,f(2)=2,f(N)=f(N-1)+f(N-2)+1$$. On day $N$, Trio will send out $f(N)$ notifications.

\noindent
How many notifications will Trio send out on the $N$:th day? To make sure the number of notifications fits on the screen, output the integer modulo $10^9+7$.


\section*{Input}
\noindent
The only and first line consists of one integer number, $N$, the day Trio is sending notifications.

\section*{Output}
\noindent
Write an integer - The total number of notifications that Trio will send that day modulo $10^9+7$.

\section*{Grading}
\noindent
Your solution will be tested on a number of test-case groups.
\noindent
To receive points for a group, your solution must correctly solve every test-case in the group.

\noindent
\begin{tabular}{| l | l | l |}
\hline
  Group & Point value & Restrictions \\ \hline
  $1$    & $20$       &  $1 \leq N \leq 3$ \\ \hline
  $2$    & $20$       &  $1 \leq N \leq 25$ \\ \hline
  $3$    & $60$       &  $1 \leq N \leq 10^6$ \\ \hline
  $4$    & $1$        &  $1 \leq N \leq 10^{18}$ \\ \hline
\end{tabular}
