\problemname{Who can win?}
\noindent
Johan and Abdullah are still playing tic-tac-toe, so now they want help figuring out who can still win in their game.
To win in tic-tac-toe you need to have three of your letter in a row, either vertically, horizontally, or diagonally.
Johan uses the letter \texttt{X} and makes the first move, and Abdullah uses the letter \texttt{O}. This implies that Johan could at most have $5$ \texttt{X}-pieces on the board, while Abdullah could at most have $4$ \texttt{O}-pieces.
It is guaranteed that no one has won.

\section*{Input}
\noindent
Input consists of a valid tic-tac-toe position, where an underscore \texttt{\_} represents an empty square, and the letters \texttt{X} and \texttt{O} represent Johan's and Abdullah's moves.
The position is described by three rows, each containing three space-separated characters. It is guaranteed that no player has already won.

\section*{Output}
\noindent
Print who can still win, if anyone.
\noindent
If both players can still win, print ``\texttt{Abdullah och Johan kan vinna}''.
If only one person can win, print their name, then ``\texttt{kan vinna}''.
If no player can win, then print ``\texttt{ingen kan vinna}''.

\section*{Grading}
\noindent
Your solution will be tested on a number of test-case groups.
\noindent
To receive points for a group, your solution must handle every test-case in the group.

\begin{tabular}{| l | l | l |}
\hline
  Group & Point value & Restrictions \\ \hline
  $1$    & $5$       &  All squares are filled \\ \hline
  $2$    & $65$       &  Either Abdullah or Johan can win, not both \\ \hline
  $3$    & $30$       &  No further restrictions \\ \hline
\end{tabular}
